---
output: rmarkdown::github_document
---

`burrp` : Tools to Import and Process [PortSwigger](https://portswigger.net/) 'Burp' Proxy Data

The Burp Suite is a set of web application and security testing tools. Combined, they intercept, record and can even transform browser traffic.

For now, the solo function - `read_burp` - expects the `request` and `response` elements of a Burp XML export file to be base 64 encoded.

Eventually there will likely be an `as_har()` function to turn the entire structure into a `HARtools` object.

To use this package you either need to have Burp proxy export files handy, use the built-in example data file or [download Burp](https://portswigger.net/burp/) and capture some web traffic and export the data.

The current Burp proxy example capture file is of a capture from the [Bloomberg Hottest Year on Record](https://www.bloomberg.com/graphics/2014-hottest-year-on-record/) scrollytelling datavis. It's a good example of how to use Burp to capture requests as you interactively work in a browser (you can get the JSON data behind the vis this way, too).

The following functions are implemented:

- `read_burp`	Read in a Burp proxy XML export file

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/burrp")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE, fig.height=6, fig.width=10}
library(httr)
library(burrp)
library(hrbrthemes) # github
library(tidyverse)

# current verison
packageVersion("burrp")

system.file("extdata", "hottest_year.xml", package="burrp") %>%
  read_burp() -> burp_df

glimpse(burp_df)

burp_df$request[[3]]

burp_df$response[[3]]

content(burp_df$response[[3]], simplifyDataFrame=TRUE) %>% 
  unnest() %>% 
  filter(key != "0") %>% 
  mutate(key=factor(key, levels=as.character(1:12), labels=month.abb)) %>% 
  mutate(color=ifelse(year=="2014", "#cb181d", "#b5b5b5")) %>% 
  mutate(size=ifelse(year=="2014", 0.5, 0.15)) %>% 
  ggplot(aes(key, value, group=year, color=color, size=size)) +
  geom_hline(yintercept = 0, size=0.2) +
  geom_line() +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_continuous(breaks=c(-1, 0, 1), labels=c("-1°F", "20th Century\nAverage", "1°F")) +
  scale_color_identity() +
  scale_size_identity() +
  labs(x=NULL, y=NULL, title="Hottest year on record (2014 in red)",
       caption="Source: Bloomberg <https://www.bloomberg.com/graphics/2014-hottest-year-on-record/>") +
  theme_ipsum_rc(grid="XY", axis="xy") +
  theme(legend.position="none")
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(burrp)
library(testthat)

date()

test_dir("tests/")
```

