---
output: rmarkdown::github_document
---

`burrp` : Tools to Import and Process [PortSwigger](https://portswigger.net/) 'Burp' Proxy Data

The Burp proxy is a web application and security testing tools. It intercepts, records and can even transform browsaer traffic.

For now, the solo function - `read_burp` - expects the `request` and `response` elements of a Burp XML export file to be base 64 encoded.

Eventually the `request` and `response` objects will be turned into `httr` compatible objects and there will be and an `as_har()` function to turn the entire structure into a `HARtools` object.

The following functions are implemented:

- `read_burp`	Read in a Burp proxy XML export file

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/burrp")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(burrp)
library(dplyr)

# current verison
packageVersion("burrp")

system.file("extdata", "burp.xml", package="burrp") %>%
  read_burp() %>%
  glimpse()
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(burrp)
library(testthat)

date()

test_dir("tests/")
```

